---
title: "Assignment_3"
author: "Maliat"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# String Manipulation

```{r, include=FALSE}
install.packages("rebus",repos = "http://cran.us.r-project.org")
library(tidyverse)
library(stringr)
library(magrittr)
library(rebus)
library(glue)
```
### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"
###Regular expression was implemented for this problem. str_detect from regular expression is used to identify "DATA" and "STATISTICS" majors.
```{r}
setwd("C:/Users/malia/OneDrive/Desktop/MSDS DATA 607")
assigment3_dat<-read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
assigment3_dat1<-c(assigment3_dat$Major)
  

```

```{r}
head(assigment3_dat1)

```



```{r}
assigment3_dat1[str_detect(assigment3_dat1,
   pattern = "DATA"
)]
```


```{r}
assigment3_dat1[str_detect(assigment3_dat1,
   pattern = "STATISTICS")]


```
### 2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

### In order to solve this problem to create a single comma separated vector, glue_collapse was used. After that c() is used to compress the data sets in a single vector.For further manipulation st_replace_all is used to clean data by removing unwanted space, brackets etc.
```{r}


FRUITS1 <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'

FRUITS1 <- str_extract_all(FRUITS1, "(.+?)+")
FRUITS1 <- unlist(FRUITS1)

FRUITS1
```



```{r}

Fruitlist1<-glue_collapse(FRUITS1,sep = ", ")
print(Fruitlist1)
```

```{r}
c(Fruitlist1)
```
```{r}
Fruitlist1<- str_replace_all(Fruitlist1, "[\\[\\]]", "") # for removing square brackets
Fruitlist1 <- str_replace_all(Fruitlist1, "[!^[:digit:]]", "") #removing digits
Fruitlist1 <- str_replace_all(Fruitlist1, "\\\n", "") #removing "\n"
Fruitlist1 <- str_replace_all(Fruitlist1, '[\"]', "'") #replacing '\"' with "'"
Fruitlist1<- trimws(Fruitlist1) #removing leading / trailing whitespace
Fruitlist1 <- str_replace_all(Fruitlist1, "\\s+", " ") #compresseng whitespace
Fruitlist1 <- str_replace_all(Fruitlist1, "' '", "','") #' ' ' --> ','
print(Fruitlist1)

```

```{r}
is.vector(Fruitlist1)
```

### 3 Describe, in words, what these expressions will match:
### (.)\1\1

### This expression will not match anything because it is incorrectly done. If it was done like this : (.)\\1\\1   it would repeat a charecter in first group then repeat it again. 

### "(.)(.)\\2\\1"
### This expression matches a first letter and a second letter in the following order: 1st letter - 2nd letter - 2nd letter - 1st letter. For instance"Beeb" "pepper".

### (..)\1
### This expression will match nothing because the correct statement looks like this:(..)\\1.if it was done correctly it will match charecters repeated twice.For instance: "LELELI".

### "(.).\\1.\\1"
### This expression will match charecter shows up 3 times with one charecter between each.For  instance: Eleven. "e" shows up three times in this word.

### "(.)(.)(.).*\\3\\2\\1"
### This expression will match three charecters in one order with * charecters between, then three charecters with three letters in the reverse order of what it started.For instance "lizpizil","bantannab"


### 4 Construct regular expressions to match words that:

###Start and end with the same character.



```{r}
word_list <- c("Apple","LIL","Orange","Blue","ELLE")  
same_char <- "^(.).*\\1$"
word_list %>% 
  str_subset(same_char)
```
### Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
repeated_thrice <- c("eleven","committee","Emimtmt")  
slicing <- "(.).\\1.\\1"
repeated_thrice %>% 
  str_subset(slicing)
```
### Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
repeated_twice <- c("church","papa","apple")  
slicing1 <- "(.)(.).*\\1"
repeated_twice %>% 
  str_subset(slicing1)
```












